Multi-level modeling with Openflexo/\FML

### 2021-10-06 6-modelpresentation.tex
consistency between figure and text: the relation between CodeArtifact and ProgrammingLanguage is "languages", but text was saying "language". Updated the text.

The \texttt{CodeArtifact} concept extends \texttt{SEArtifact}, and defines a relation \texttt{language} to \texttt{ProgrammingLanguage} with 1..* cardinality (\textbf{S4}).

\textbf{S5} is more ambiguous as a task type \texttt{CodingTask} defines one or more programming languages but produces code which is expressed in one language only. This requirement is captured through the redefinition of the behavior \texttt{declaresRequiredProducedArtifacts} where programming language should also match.
\textbf{S6} is guaranteed though the \texttt{language} relation defined in \texttt{CodeArtifact} and the following invariant declared in \texttt{CodeArtifact}:
\begin{lstlisting}
forEach (artifactType : types) {
  assert !(artifactType instanceof CodeArtifactType) | artifactType.doesImplement(languages)
}
\end{lstlisting}

>>>>

The \texttt{CodeArtifact} concept extends \texttt{SEArtifact}, and defines a relation \texttt{languages} to \texttt{ProgrammingLanguage} with 1..* cardinality (\textbf{S4}).

\textbf{S5} is more ambiguous as a task type \texttt{CodingTask} defines one or more programming languages but produces code which is expressed in one language only. This requirement is captured through the redefinition of the behavior \texttt{declaresRequiredProducedArtifacts} where programming language should also match.
\textbf{S6} is guaranteed though the \texttt{languages} relation defined in \texttt{CodeArtifact} and the following invariant declared in \texttt{CodeArtifact}:
\begin{lstlisting}
forEach (artifactType : types) {
  assert !(artifactType instanceof CodeArtifactType) | artifactType.doesImplement(languages)
}
\end{lstlisting}
